### 2020-03-13 outline.tex
small change

\begin{prop}
  There is a fully faithful inclusion $\bang_{(-)} : \Sa \to \DirSeries$ given by
  $$X \mapsto \begin{tikzcd} X \arrow[d, "!_X"] \\ \ast \end{tikzcd}$$
\end{prop}

>>>>

\begin{prop}
  There is a fully faithful inclusion $\bang_{(-)} : \Sa \to \DirSeries$ given by
  $$X \mapsto \begin{tikzcd} X \arrow[d, "!_X"] \\ \ast \end{tikzcd}$$
  This functor preserves all limits and weakly contractible colimits
\end{prop}
\begin{proof}
  This functor preserves all limits because it has a left adjoint given by sending $\pi : E \to B$ to $E$ (in terms of families, this sends the family $E_b$ to the sum $\sum_{b : B} E_b$).

  To see that it preserves weakly contractible colimits, recall that colimits in $H^{\downarrow}$ are calculated pointwise. It remains to show, then, that the map
  \[
    \begin{tikzcd}
    \colim S_i \arrow[r, equals] \arrow[d] & \colim S_i \arrow[d] \\
    \colim \ast \arrow[r] & \ast 
    \end{tikzcd}
  \]
  is an equivalence in $H^{\downarrow}$, for which it suffices to show that $\colim \ast$ is contractible. But the colimit of the terminal diagram is the (Kan-fibrant replacement of) its indexing simplicial set -- since we assumed the diagram was weakly contractible, $\colim \ast$ is contractible.
\end{proof}
